\toadd{intro}
\section{Desired Properties}
  \subsection{Verifiability}\label{Subsection:verif}
  A protocol is verifiable if its output can be inspected to confirm that the
  protocol was carried out correctly. A simple example of this is signing a
  message with the private key associated with a well-known public key: Anyone
  who knows the public key can verify the validity of the signature.

  Voting protocols can be evaluated in their provision of three different
  kinds of verifiability \cite{kremer_election_2010}: \emph{individual}
  verifiability ensures that a voter can verify their vote was included
  correctly. \emph{Universal} verifiability requires that anybody can verify
  the election result correctly represents the collection of ballots cast.
  Finally, \emph{Eligibility} verifiability allows anybody to verify that
  only eligible voters voted, and that each voter voted only once.

  % Dissent \cite{verdict}
  % and the Neff shuffle \cite{neff} both use zero-knowledge
  % proofs to achieve verifiability.

  \subsection{Anonymity}\label{Subsection:anon}
  Members of any group often face reprocussions if they participate in group
  governance in ways that run contrary to the interests of other members of
  the group. For this reason, election protocols often incorporate some notion
  of anonymity. A protocol guarantees \emph{anonymity} in some operation a
  client can complete if the output of that operation is unlinkable (or, more
  precisely, cryptographically very difficult to link) to the participant who
  completed it\cite{ford_hiding_2014}.

  We are interested in two types of anonymity: First, within an election,
  each voter's confidentiality should be preserved. Second, the instigator of an
  election, who may also be the author of the proposed petition, should be
  anonymous.

  \section{Threat Models}\label{Section:threats}
  Newly available information about vulnerabilities and global-scale
  surveillance in today's centralized internet infrastructure has brought new
  security considerations and threat models to the foreground of networked
  system research. It has rendered a swath of anonymity and voting tools
  obsolete, and poses a significant threat to those that remain. Group
  management protocols aimed at dissidents must take this into account.

  \subsection{Byzantine Fault Tolerance}
    In shifting our focus from offline voting algorithms to networked protocols,
    we must consider several types of disruptions not taken into account by
    those algorithms. In particular, any member tasked with ``broadcasting'' a
    message may equivocate, sending different values to different participants.
    Existing work on distributed consensus provides various approaches to these
    problems.

    Paxos and many similar protocols makes the simplifying assumption that all
    nodes in the system are honest --- the only faults considered are those
    triggered by nodes suddenly going offline. If nodes may be malicious, they
    may ``fail'' not just by disappearing, but by forging messages in an effort
    to influence the consensus value. \emph{Byzantine} consensus protocols allow
    the honest nodes in a system to arrive at a canonical value, so long as some
    minimum portion of nodes are honest. The original Paxos can
    accommodate Byzantine failures if an additional verification stage, in which
    all Acceptors communicate with all other Acceptors in order to detect
    equivocation, is added before the final step \cite{castro_practical_1999}.
    Additional optimizations to regular and Byzantine Paxos have also been
    developed \cite{lamport_fast_2006}. If the adversary can not only send
    arbitrary messages but also monitor messages exchanged among other nodes,
    additional attacks are possible. One approach to this divides the nodes into
    small quorums in an effort to contain malicious nodes \cite{king_load_2011}
    while also providing better scalability than solutions that require
    all-to-all communication to thwart equivocators.

    In both its standard and Byzantine formulations, the distributed consensus
    problem assumes discrepancies in the record will only be due to faults ---
    that is, each assumes all honest participants either agree on what the value
    should be or agree to accept the value reported by the nodes who do know the
    value.  In the election of rotating leaders or servers, the correct value is
    not knowable a priori. If our leader election algorithm is modeled on other
    election protocols, it must be assumed that honest nodes may disagree on
    which servers they wish to elect.

  \subsection{Global Passive Adversary}
    To provide anonymity from an adversary like the N.S.A., a modern anonymity
    protocol must protect against several forms of attacks. Feigenbaum et.
    al.\cite{feigenbaum_seeking_2013} highlight several specific attacks to
    which onion routing is vulnerable:
    \paragraph{Global traffic analysis:}
    If the adversary can monitor most of the traffic on the internet globally,
    the adversary can with high probability see the link from Alicia to the Tor
    network and from the Tor exit relay to Badru. This means the adversary can
    observe that the messages Alicia sends correspond to messages Badru receives
    some short amount of time later. Even if the messages themselves are
    encrypted, the adversary can analyze the lengths and other metadata about
    the messages to correlate this traffic.
    % TODO: Move to non-goals; possibly add self-ID
    % \paragraph{Active attacks:}
    % Global traffic analysis attacks only require the adversary to be able to
    % monitor global traffic. If the adversary can also modify or generate
    % traffic, several other attacks are possible. The adversary can launch
    % \emph{man-in-the-middle} (MITM) attacks in which it impersonates Alicia,
    % Badru, or one or more Tor nodes. The adversary can launch \emph{Sybil}
    % attacks, in which many different Tor clients controlled by the same
    % adversary join the network as individual clients. Either of these can be
    % used to create \emph{Denial-of-Service} (DoS) attacks, which might either
    % prevent users from connecting to Tor at all, or force Tor traffic to go
    % through particular, potentially adversary-controlled, Tor nodes ---
    % de-anonymizing the users.
    \paragraph{Intersection attacks:}
    In general, it is possible to tell when users are using an anonymity service
    --- the anonymity comes from the difficulty of linking any particular user
    to particular messages produced by the service. Over time, however, the
    client set of an anonymity service is unlikely to remain fixed. A passive
    adversary monitoring the outputs of an anonymity service as well as the set
    of users connected can narrow the set of users who potentially, for example,
    updated a particular blog with a static pseudonym, by excluding users  not
    online during all updates to the blog.

  \subsection{The Trouble with Relays}
  \label{Subsection:Relays}
  \todoword{copy edit Tor vs. Dissent}
    One potential approach to making Dissent widely available would be to have
    well-known, globally dispersed Dissent servers available for clients to
    connect to, similar to the current state of Tor. Any such well-known server
    list, however, is susceptible to blocking by internet service providers. It
    would therefore be preferable to have servers be short-lived, or at least
    not well known. Since Dissent takes place over regular TCP connections,
    detecting that the protocol is being executed without knowledge of the
    addresses of servers would be difficult to accomplish without a great number
    of false positives \cite{houmansadr_parrot_2013}, so this may be enough to
    realistically preclude most attempts to block access to the protocol
    entirely.  Additionally, while the current version of Dissent guarantees
    that malicious servers cannot deanonymize a client without the cooperation
    of all servers, and guarantees that disrupting servers can be exposed, it
    provides no way to remove a disrupting or malicious server form the system.

    One way to resolve these problems would be to have clusters of Dissent
    clients elect temporary servers among themselves, allowing servers to either
    step down (e.g., by going offline) or be impeached by some portion of the
    clients.  Doing so in a truly decentralized and fair fashion is a
    non-trivial problem.  We consider several other areas of research relevant
    to solving it.


