In this chapter, we outline a general specification for verifiable, anonymous,
and fully decentralized election protocols. For simplicity, we assume all votes
have only two options (ratify or not), but not that it can be proven that any
other multiple choice ballots can be constructed from these components and thus
our analysis is fully generalizable.
% \section{Terminology}
\section{Terminology and Data Structures}
\begin{itemize}
  \item This protocol operates at the level of a \texttt{Cluster} of
    \texttt{Node}s.  A \texttt{Peer} is a \texttt{Node} that is a member of a
    particular \texttt{Cluster}. It may be voted out of a cluster. New nodes
    become \texttt{Peer}s if their joining is approved by the existing cluster.

  \item A \texttt{Manifest} defines the group configuration and consists of
  \begin{itemize}
    \item A \texttt{Roster}, representing the set of eligible voters
      % mapping public keys to IP addresses for all \texttt{Client}s,
    \item A map \texttt{Committees} mapping names of elected statuses to sets of
      elements of the \texttt{Roster}. For example, \texttt{Committees} might
      consist of the key ``\texttt{servers}'', with the value $\{A, B, C\}$, where
      $A, B,$ and $C$ are the participants listed in $R$ which have been elected
      to act as \texttt{servers} in an instance of Dissent in Numbers.
    \item A function $t : E \to (\{\textsc{True, False, Invalid}\}, P)$
      where $E$ is the set of all \emph{Election State}s, and $P$ is the set
      of all possible proofs of correctness of the result. That is, if $t(g) =
      \textsc{True}$ for some outcome $g$, then the proposal corresponding to
      $g$\todo{TODO: clarify, or define after election} passes.
      % should be adopted at the specified expiration round.
      A plausible example is the function which
      specifies what proportion of \texttt{Peer}s must agree to a change in the
      composition of the \texttt{Roster} in order for the change to take effect.
  \end{itemize}
  \item A \texttt{Petition} is a proposal to change the \texttt{Manifest}. It
    consists of
    \begin{itemize}
      \item An \emph{Instigator}, the \texttt{Peer} who proposed the
        \texttt{Petition}. This information is not publicly associated with
        the \texttt{Petition}.
      \item A unique identifier $L$, which is public
      \item A proposed new \texttt{Manifest},
      \item An expiration condition, defining when the vote on the petition
        should end.
    \end{itemize}
  \item A \texttt{Ballot} encodes information about the eligibility of the voter,
    and information about the voter's preference. To determine the results of
    the elction while providing the verifiability properties discussed in
    Section~\ref{Subsection:verif}, there must be a public record of some
    aggregate information about each: An auditor must be able to tell that every
    voter was eligible, and also what the outcome of the election was. To
    provide voter confidentiality, we must provide a way for each voter to
    provide both bits of information without exposing the correlation between
    the two. In other words, if Badru wants to vote for Alicia to be president,
    Badru must convey that Badru (or someone with Badru's credentials) voted,
    and that a vote has been cast for Alicia, without revealing that Badru cast
    a vote for Alicia. We can represent the information Badru provides as a
    \emph{Vote} tuple $(sig, vote)$, where $sig$ encodes Badru's credentials and
    $vote$ encodes his candidate choice.

    To provide the necessary information while preserving his
    confidentiality, Badru must encrypt part or all of his ballot.
    We show
    in Appendix~\ref{Appendix:SecretProof}\todosubst{I think this is actually
    only true if people vote at different times} that it is impossible to design
    a Byzantine Fault Tolerant protocol where both are kept secret. This leaves
    two possibilities:
    Either Badru can encode his credentials in a $sig$ that is anonymous
    (c.f. \cite{lrs})
    % \todogrunt{talk about LRS/refer to it here},
    or he can encrypt $vote$ so that Badru's choice of candidates can only be
    decyphered in aggregate, once the connection to Badru's public signature has
    been lost.


    % is a tuple $(L, M', rid)$, where $L$ is a unique
    % bytestring selected arbitrarily by the instigator, $M$ is the current
    % manifest of the cluster, $M'$ is a proposed new manifest, and $rid$ is a
    % Dissent round number at least $|M.R|$ rounds in the future.\todo{future is
    % undefined wrt non-stateful petition}
    %
\end{itemize}

\section{States}
\begin{itemize}
  \item A \emph{State} is a tuple $(M, r)$ defining the current cluster, where
    $M$ is a \texttt{Manifest}, and $r$ is a monotonically increasing unique
    state identifier (i.e., a logical clock)\tocite.

  % \item A \emph{Proposal} is a stateful \texttt{Petition}, that is, a tuple $(S,
  %   P)$, where $S$ is the current state and $P$ is a petition.
  %   \todo[color=orange,inline,caption={}]{TODO: What if config changes during
  %   election?}
  %
  \item An \emph{Election} encompasses the operation of the protocol between
    when a \texttt{Petition} $P$ is first proposed and the round
    $P$.\texttt{rid} --- that is, the portion of the protocol where members are
    aware that that \texttt{P} is being considered, but in which no member knows
    the outcome of the election.

  \item The \emph{Election State} can be described by a tuple
    $((M, r), P, V)$, where $(M, r)$ is the current \emph{State}, $P$ is the
    \texttt{Petition} being voted on, and $V$ is a collection of \texttt{Votes}
    that have been cast thus far.

    %  linkable ring signatures from
    % members of $S.M$ according to link scope
    % $P.L$.\todo[inline,color=orange]{this isn't a state\ldots}

  % \item A \emph{result} is a tuple $(M, G, rid)$ defining a manifest $M$ and a
  %   set of signatures $G$.
  %
  % \item An \emph{instigator} is a member who initiates an election.
  %
\end{itemize}

\section{Functions}
Each \texttt{Peer} should implement the following functions:
Within finite time and in a way that is fair, every \texttt{Peer} should be able
to call each of the following functions:
\begin{itemize}
  % \item The \textsc{Sign} function, provided by \cite{golrs}, takes in a set of
  %   public keys $S$\todo{TODO:  Don't overload $S$}, a link scope $L$, a
  %   private key $k$ corresponding to an element of $S$, and a petition $P$ to be
  %   signed.
  \item \textsc{Propose}(\texttt{Petition} $P$): broadcasts $P$ to the cluster
    and initiates an \emph{Election}
  \item \textsc{Vote}$_{\texttt{State} (M, r)}$(\texttt{Petition} $P$), which
    constructs a ballot ($sig$, $vote$) and broadcasts it to the cluster in
    conjunction with $P$
  \item \textsc{Evaluate}$_{\texttt{State} (M,r)}$(\texttt{Petition} $P$,
    \texttt{Vote}s $V$) $\to (\{\textsc{Unfinished}, \textsc{Valid},
    \textsc{Invalid}\}, proof$: Given an election state, every peer
    should be able to determine whether the election has ended, and if it has,
    what the result was. If it cannot, or if any part of the election state is
    invalid, it should be able to provide a $proof$ of misbehavior.
  \item \textsc{Evaluate}$_{\texttt{State} (M,r)}$(\texttt{Petition}
    $P$, \texttt{Vote} $v$) $\to$ (\{\textsc{True, False}\}, $proof$) should
    return (\textsc{True}, $proof$) if $v$ was produced by a valid \texttt{Peer}
    according to $(M,r)$, and is a vote on $P$. Otherwise, \textsc{True} and a
    proof of misbehavior should be produced.
\end{itemize}
% \begin{algorithm}
  % \Kwin{
  % ohai
  % \SetAlgoLined
  % \KwIn{this text}
  % \KwOut{how to}
  %
  % initialization\;
  % \While{hello}{
  %   face\;
  %   \eIf{udners}{
  %     sauce\;
  %   }{
  %     parse\;
  %   }
  % }
%   \caption{Evaluate}
% \end{algorithm}


\section{Formal Properties}
% \toadd{clean up embedded results defs etc.}
% \paragraph{Proposition 1:}
% \begin{theorem}The \emph{Election state} of any \emph{Election} at
% any time is well defined. \end{theorem}
% \begin{proof}This follows from properties of peer-to-peer Dissent \cite{sec}.
%   The \emph{Election State} can only be updated by transmission of messages
%   (votes) over Dissent. Recall that communication proceeds in serialized
%   \emph{rounds}, so by Theorem~\ref{theorem:rounds},\todo{TODO finish}
% \end{proof}
%
  \subsection{Verifiability}\label{Subsection:verif}
    \subsubsection{Individual}
    A group management protocol provides \emph{individual verifiability} if, in
    any Election State $((M,r), P, V)$, any member $u$
    either knows its own vote is correctly represented in $V$ (that is, either
    $u$ voted and $u$'s
    signature for $P.L$\todo{TODO: more params; define lrs} is contained in $G$,
    or $u$ did not vote and $u$'s signature is absent from $G$), or can produce
    a zero-knowledge proof that the Election State is invalid.\todo{TODO: define
    invalid}

    % Our protocol provides individual verifiability.
    %
    % --- this follows from the
    % properties of Dissent in Numbers and of linkable ring signatures.%: Since every
    % \paragraph{Lemma 1:} There is a well-defined state.
    %
    % \paragraph{Lemma 1:} Given accurate knowledge of the current election state
    % $(S, P, G)$, a \texttt{Member} $m$ can call
    % $m$.\textsc{Sign}($S.M.\texttt{Roster}.keys$,$P.\texttt{LinkScope}$,$m$.$k$,
    % $P$) to produce a signature $s$, then examine $G$ to see if it contains $s$.
    % By properties of linkable ring signatures,
    %

    \subsubsection{Universal}
    A group management protocol provides \emph{universal verifiability} if, in
    any finished election state, $((M,r), P, V)$%result $r = (M, B, G, rid)$,
    anybody can verify that $V$ is a valid signing of $P$ or else produce a
    proof that it is not. Consequently, any auditor (member or otherwise) can
    verify the canonical value of $M.t(G)$.

    % Our protocol provides universal verifiability.%:

    \subsubsection{Eligibility}
    A group management protocol provides \emph{eligibility verifiability} if, in
    any finished election state, anybody can verify that all elements of $V$
    were cast by \texttt{Member}s of the current cluster.
  \subsection{Anonymity}
  \todo[color=orange,inline,caption={}]{TODO: formalize in terms of games}
    \subsubsection{For Instigators}
    A group management protocol provides \emph{instigator anonymity} if, during
    and after any election, no member and no outside observer can determine
    which member proposed the ballot in question.

    % Our protocol provides this through Dissent in Numbers.
    \subsubsection{Of Ballots}
    A group management protocol provides \emph{secret ballots} if, during and
    after any election, either no outside observer can reconstruct which member
    submitted which vote, or no outside observer can reconstruct how any
    member voted. The same restrictions apply to knowledge gained by other
    participants, except that each member can trivially reconstruct its own vote.

    % Our protocol provides this --- it follows directly from the properties of
    % linkable ring signatures.
% \subsection{Performance Notes}
% Any changes to the arrangement of servers in Dissent in Numbers requires an
% expensive, serial shuffle. Our protocol provides a way to change the topology
% without having to redo the shuffle, so long as the client set remains the same.
%
% This allows us to retain many of the stronger security properties of Hardened
% Dissent\cite{sec} while also achieving the performance benefits
% of Dissent in Numbers and Verdict in typical usage.
